Learned image compression

### 2023-03-14 paper/paper.tex
Add abstract, sort + format references

% Title.
% ------
\title{Learned image compression}
%
% Single address.
% ---------------
\name{Juha Ylikoski, Teemu Eerola, Nardos Estifanos}
\address{juha.ylikoski@tuni.fi, teemu.eerola@tuni.fi, nardos.estifanos@tuni.fi}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
The abstract should appear at the top of the left-hand column of text, about
0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
beginning of the main text.  The abstract should contain about 100 to 150
words, and should be identical to the abstract text submitted electronically
along with the paper cover sheet.  All manuscripts must be in English, printed
in black ink.
\end{abstract}
%
\begin{keywords}
Learned image compression
\end{keywords}
%

>>>>

% Title.
% ------
\title{Learned image compression}
%
% Single address.
% ---------------
\name{Juha Ylikoski, Teemu Eerola, Nardos Estifanos}
\address{juha.ylikoski@tuni.fi, teemu.eerola@tuni.fi, nardos.estifanos@tuni.fi}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
Image compression has had some major new ideas in forms of learned image compression. 
Especially the neural network based learned image compression methods have achieved even better performance than the more traditional manually designed lossy image compression models.
These new methods are not without their own problems. The large neural network based models can achieve remarkable compression ratios and perceived image quality, but have suffered widely form being too computationally expensive to be usable.

In this work we are reviewing and trying to replicate one of these methods which claims good quality, compression ratio and speed.
\end{abstract}
%
\begin{keywords}
Learned image compression, ELIC Efficient Learned Image Compression
\end{keywords}
%
